%-------------------------
% Resume in Latex
% Author : Uddhav
% Based on: https://github.com/jakegut/resume (which was based on https://github.com/sb2nov/resume)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT --------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \vspace{-4pt}
  \color{gray}
  \item
\end{flushright}

\vspace{-35pt}

\begin{center}
    \textbf{\Huge \scshape Uddhav Pawar} \\ \vspace{8pt}
    \small 
    \faIcon{github}
    \href{https://github.com/uddhav29}{\underline{github.com/uddhav29}} $  $
    \faIcon{linkedin}
    \href{https://www.linkedin.com/in/uddhav-pawar/}{\underline{linkedin.com/in/uddhavpawar}} $  $
    \faIcon{envelope}
    \href{mailto:uddhavpawar@outlook.in}
    {\underline{uddhavpawar@outlook.in}} $  $
    \faIcon{phone}
    {\underline{+91-9423424428}} $  $
\end{center}

% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: Golang, Java, C/C++, JavaScript/TypeScript} \\
     
     \textbf{Tools and Frameworks}{: Git/GitHub, Distributed Systems(Raft), Spring Boot, Terraform, Kubernetes, Docker, AWS, Spinnaker, Jenkins, OAuth, JWT, MVC frameworks, Maven, MongoDB, DynamoDB, Unix Shell, VS Code, IntelliJ IDEA}
     
     % \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     
     % \textbf{Libraries}{: pandas, NumPy, Matplotlib}
     
    }}
 \end{itemize}

 % -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart

        \resumeProjectHeading
          {\textbf{\large Salesforce} $|$ \footnotesize\emph{Senior Member of Technical Staff}\vspace{3pt}}{Present}

        \resumeProjectHeading
        {\textbf{Vault Accelerator - secrets management} $|$ \footnotesize\emph{Golang, DynamoDB, AWS(EKS, EC2, IAM), Kubernetes, Terraform, Git}}{}
          \resumeItemListStart
            \resumeItem{Designed and implemented a horizontally scalable solution that \textbf{increased} the API request handling capacity of the Secrets Management application\textbf{ by 20x from 300 RPS to more than 6,000 RPS}, processing more than \textbf{400 million requests per day.}}
            \resumeItem{Significant \textbf{contribution to open source code} by implementing an alternative \textbf{read replica-based solution} to the traditional Raft, leader-follower model, resulting in improved system performance and capacity.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Backup and Restore for Vault} $|$ \footnotesize\emph{Golang, AWS(S3, EC2, IAM), Docker, Git}}{}
          \resumeItemListStart
            \resumeItem{Successfully designed and implemented a \textbf{secure solution} for taking remote backups of secrets services running in first-party data centers and restoring them to public cloud providers (AWS)}
            \resumeItem{Built a solution that provides \textbf{IAM credentials to containers running in a DIY Kubernetes cluster} (not EKS) while maintaining least privilege security using IAM roles.}\vspace{8pt}
        \resumeItemListEnd

         \resumeProjectHeading
          {\textbf{\large Principal Financial Group} $|$ \footnotesize\emph{SDE 2}\vspace{3pt}}{April 2021}

          
         \resumeProjectHeading
        {\textbf{Data Inquiry Tool} $|$ \footnotesize\emph{Java, SpringBoot, Maven, Git}}{}
          \resumeItemListStart
            \resumeItem{Developed an in-house search tool that provides personal data of customers across all databases in the organization, using \textbf{Graph-data structure and Spring Boot.}}
            \resumeItem{Potential savings for the company- about \textbf{3mn dollars} in licensing and administrative fines of data protection act.}\vspace{-15pt}
        \resumeItemListEnd

         \resumeProjectHeading
        {\textbf{Disbursement Services} $|$ \footnotesize\emph{Java, SpringBoot, AWS(Lambada, IAM, API Gateway), CDK, Maven, Git}}{}
          \resumeItemListStart
            \resumeItem{Developed payment disbursement APIs serving \textbf{300K requests/day} across 2 clients, using Spring Boot and Cloud Foundry.}
            \resumeItem{Enhanced customer experience by adding reporting features, resulting in \textbf{63\% reduced number} of calls asking for payment updates.}
        \resumeItemListEnd
          
    \resumeSubHeadingListEnd 

% -------------------- ACHIEVEMENTS --------------------
\section{Achievements}
    \resumeItemListStart
            \resumeItem{HackerRank: \textbf{5 Star Gold Badge} in Problem-Solving with world rank in \textbf{top 1\% out of 860k} participants in Data Structures problem-solving. \textbf{5 Star Gold Badge} in \textbf{Java}. \textbf{@pawar\_uddhav}}\vspace{-5pt}
            \resumeItem{\textbf{Promoted} within 5-6 quarters of joining Salesforce to the senior role because of the impact of projects built.}\vspace{-5pt}
            \resumeItem{\textbf{AWS Certified Developer}}\vspace{-5pt}
            \resumeItem{\textbf{Cleared} InterviewBit’s Scaler coding contest, was selected amongst the \textbf{top 300 out of 16k} participants.}\vspace{-5pt}
            \resumeItem{\textbf{Impactful project of the year by PFG Pune}; awarded a total cash prize of INR 20k for ‘Data Inquiry Tool’.}\vspace{-5pt}
            \resumeItem{\textbf{Rising Star Award by PFG Pune} for delivering \textbf{2.2x of expected} in 2018, amid 500+ employees.}\vspace{-5pt}
        \resumeItemListEnd

% -------------------- PROJECTS --------------------

\section{Projects}
    \resumeSubHeadingListStart
    
          \resumeItem
          {\textbf{Online Complaint Portal -
          \small }A website development hackathon organized by IIT Bombay, developed an online platform for responsibly and anonymously lodging corruption claims against government officials and \textbf{emerged as a finalist}.}\vspace{-4pt}
          \resumeItem
          {\textbf{AWS Infrastructure as code -
          \small }Developed a Java application for defining cloud infrastructure in code using aws-cdk which creates a REST endpoint using API Gateway, validates request payload, and integrates it with the AWS lambda function.}\vspace{-4pt}
          \resumeItem
          {\textbf{PFG Events -
          \small }Developed a mobile application to track event attendance and post-event analysis, using Flutter and Firebase.}\vspace{-1pt}
          
    \resumeSubHeadingListEnd
    
    % -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {B.E.(IT), Government College of Engineering, Aurangabad}{2013 - 2017}
     {  }{  }  

  \resumeSubHeadingListEnd

\end{document}
